\documentclass[letter, 14pt]{article}
\usepackage{TLCresume}
\begin{document}


\subsection{Research Engineer \hfill \textit{\textmd{02/25 - Present/}}}
\subtext{\href{https://www.linkedin.com/company/huawei}{\color{black}{Huawei}} \hfill}
\begin{zitemize}
\item Article on measuring phonetic distance between cross-lingual character pairs, at IEEE SIU 2025 Conference. \href{https://ieeexplore.ieee.org/abstract/document/11112305}{\color{black}\externallink} \\
\item ~1\% improvement to accuracy in ranking pipeline via the addition of phonetic feature
\item ~2\% improvement to translation accuracy on queries belonging Cyrillic and Arabic alphabets.
\item Augmentation of queries via recall strategies on translation dictionaries.
\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{AI Researcher \& Engineer \hfill \textit{\textmd{10/23 - 10/24}}}
\subtext{\href{https://www.linkedin.com/company/mogram}{\color{black}{Mogram}} \hfill}
\begin{zitemize}
\item Mass \& Tumour \& Calcification segmentation with various encoder-decoder networks.
\item Used patch-based transformer encoder-decoder network to enhance f1 and box f1 scores by around 10\%.
\item R\&D of the segmentation training pipeline with MLflow.
\item Combined \href{https://www.epfl.ch/labs/ivrl/research/slic-superpixels/}{\color{black}{SLIC}} algorithm with adaptive thresholding to gain roughly 10x speed over CPU-bound processes.
\item Design of on-premise service authentication and encryption routines.
\item Anonymization of the DICOM file structure and organization of datasets.
\item Resolved Docker and MongoDB issues in a remote setup. 
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{AI Team Member \& Participant \& Lecturer \hfill\textit{\textmd{{\tiny$\sim$} 02/21 - Present}}}
\subtext{\href{https://inzva.com/}{\color{black}{Inzva}}}
\begin{zitemize}
\item Design and tracking of learning materials as a member of the AI Team.
\item Gave lectures on Structures of ML projects and Computer Vision Fundamentals.
\item Google Tensorflow Developer \& DL Specialization certificates.
\item Worked with Mamba architecture on State Space Tracking/Modelling of Transformer-based LLMs.
\item Application of various deep learning models and study programs to solve real-life and designed challenges for peer learning.
\end{zitemize}


%====================
% EXPERIENCE C
%====================
\subsection{AI Research Student \hfill \textit{\textmd{ 06/22 - 10/23}}}
\subtext{\href{https://www.asillab.com/}{{\color{black}{ASIL Laboratories}}} \hfill}
\begin{zitemize}
\item Dataset creation, labelling \& preprocessing of medical histopathology images.
\item Segmentation for pixel-wise tumour detection, f1 over 70\% with unified resampling for post-processing.
\item Image augmentation techniques with Autoencoder and Diffusion models
\item Published abstract on 
\href{https://arxiv.org/abs/2504.05219}{\color{black}{arxiv. \externallink}}
\end{zitemize}


%====================
% EXPERIENCE D
%====================
\subsection{Machine Learning Intern \hfill \textit{\textmd{ 07/22 - 08/22}}}
\subtext{\href{https://optiwisdom.com/}{{\color{black}{Optiwisdom}}} \hfill}
\begin{zitemize}
\item Integration of the customer database into NoSql.
\item Various ML methods (boosting \& tree algorithms) for revenue prediction.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%%% \subsection{Intern / Machine Workshop \hfill \textit{\textmd{ 01/2022 - %%% 02/2022 }}}
%%% \subtext{\href{http://www.pro-ser.com/index_en.htm}{{\color{black}{Pro-Ser Laboratory Equipments and Automation}}}}
%%% \begin{zitemize}
%%% \item Manufacturing processes of industrial test devices.
%%% \item Machine part drawings on Solidworks.
%%% \item API for the government wastewater surveillance system.
%%% \end{zitemize}


%====================
% EXPERIENCE F
%==================== 
\subsection{Other Study}
\subtext{}
\begin{zitemize}
\item Worked on 3D car localization with sensor fusion and YOLO 
 \href{https://www.youtube.com/watch?v=FBLalZQ7VFo}{\color{black}\externallink}
\item Building an autonomous microscope to classify fungi cells for the graduation project.
\href{https://github.com/denizberkin/grad-project-without-database}{\color{black}\externallink}
\item Deep Learning Specialization courses and certificate by Andrew Ng. 
\href{https://www.coursera.org/account/accomplishments/specialization/certificate/WNJCS69WKCQ8}{\color{black}\externallink}
\item Tensorflow Developer courses and certificate by Laurence Moroney. 
\href{https://www.coursera.org/account/accomplishments/specialization/certificate/3WKMBQ8CVFY4}{\color{black}\externallink}
\end{zitemize}


\end{document}